\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}

\title{CSC111 Winter 2024 Project 1}
\author{Ali Towaiji, Tanay Langhe}
\date{\today}

\begin{document}
\maketitle

\section*{Enhancements}


\begin{enumerate}

\item Math class puzzle
	\begin{itemize}
	\item in this puzzle the player must enter the math classroom and answer a math question in order to recive the key.
	\item This key is then used to enter the locked room which is where you find your TCard
	\item Complexity level high:
	\item this puzzle is high complexity level since it required the management of both the locations items and the players items
	\item and what the world allowed so it used many classes in order to function.
	\item also it focused on whether the it was that correct item and if it was used in the correct location.
	\item secondly, the questions produced are not hardecoded but come from the item.txt file meaning to get the right question
	\item and answer also requires setting up and accesing the correct attributed within the class. Then by using the pick-up
	\item function it further complicates the code.
	% Feel free to add more subheadings if you need
	\end{itemize}

\item Find KitKat in order to recieve Lucky Pencil
	\begin{itemize}
	\item in order to acquire your lucky pencil you need to first enter the bathroom to find a person who for some
	\item reason has it. They would not let go of the pencil unless you give them a sweet in return. this sweet can
	\item be found in a robarts study room where you have to solve a puzzle in order to open a lock that has the kit kat
	\item inside it and then give it to the person, so you finally get your Lucky Pencil
	\item Complexity level high:
	\item the complexity is High because firstly, it requires the management of both the locations items and the
	\item players items and what the world allowed so it used many classes in order to function.
	\item also it focused on whether the it was that correct item and if it was used in the correct location.
	\item secondly, the questions produced are not hardecoded but come from the item.txt file meaning to get the right question
	\item and answer also requires setting up and accesing the correct attributed within the class.
	\item after doing the puzzle, doing the use command KitKat to trade further complexifies the code, requiiring the introduction
	\item of a new function that works in tandem with the several differnt class attributes accessed and chnaged to operate
	\item correctly.
	% Feel free to add more subheadings if you feel the need
	\end{itemize}

\item Figure out passcode to IPad in dorm
	\begin{itemize}
	\item in this puzzle you need to use your Ipad in order to print your cheat sheet. Although first you have to find
	\item your ipad in your dorm room. after doing so you need to solve a quick puzzle in order to unlock it so that you
	\item can use it to print your cheat sheet at the robarts printing room.
	\item Complexity level high:
	\item the complexity is High because firstly, because it required the management of both the locations items and the
	\item players items and what the world allowed, so it used many classes in order to function.
	\item also it focused on whether the it was that correct item and if it was used in the correct location.
	\item secondly, the questions produced are not hardecoded but come from the item.txt file meaning to get the right question
	\item and answer also requires setting up and accesing the correct attributed within the class.
	\item after doing the puzzle, doing the use command on the IPad to trade it further complexifies the code, requiiring
	\item the introduction of a new function that works in tandem with the several differnt class attributes
	\item accessed and changed to operate correctly.
	% Feel free to add more subheadings if you feel the need
	\end{itemize}


\item Map Maker
	\begin{itemize}
	\item this enhancement adds the ability to check the map and the area numbers.
	\item it also shows the areas that are blocked (marked by -1).
	\item also it shows an X at the position which the player is in.
	\item Complexity level low:
	\item the map maker function was not so difficult it just required a function that looped through the values of the
	\item map and had an if statement that checked where the player is and marked them on them map with an X
	% Feel free to add more subheadings if you feel the need
	\end{itemize}


\end{enumerate}


\section*{Extra Gameplay Files}

If you have any extra \texttt{gameplay\#.txt} files, describe them below.

\end{document}
